Paper 1 Analysis

### 2017-01-19 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Demo of indexing.

  scale_color_manual(
    name = "",
    labels = c("Historical", "Fitted"),
    values=c("black", "black")
  ) +
  scale_size_manual(
    name = "",
    labels = c("Historical", "Fitted"),
    values = c(0.2, 0.2)) +
  scale_linetype_manual( 
    name = "",
    labels = c("Historical", "Fitted"),
    values=c(1,2) ) + 
  labs(x="", y="Indexed GDP (1960 = 1)") +

>>>>

  scale_color_manual(
    name = "",
    labels = c("Fitted", "Historical"),
    values=c("black", "black")
  ) +
  scale_size_manual(
    name = "",
    labels = c("Fitted", "Historical"),
    values = c(0.2, 0.2)) +
  scale_linetype_manual( 
    name = "",
    labels = c("Fitted", "Historical"),
    values=c(1,2) ) + 
  labs(x="", y="Indexed GDP (1960 = 1)") +
